\vspace{60pt}\\ \huge \bfseries Skedge \\ \vspace{10pt} \Large Smarter course scheduling for our University

### 2016-04-13 analytics/dsl.tex
chapter 4 done

\begin{figure}
  \centering
  \vspace{-10pt}

  \begin{subfigure}[w]{0.85\textwidth}
    \includegraphics[width=1.00\textwidth]{images/graph/search_dt}

    \caption{Etc}
    \label{fig:sc-graph}
  \end{subfigure}

  \\
  \vspace{30pt}

  \begin{subfigure}[w]{0.75\textwidth}
    \includegraphics[width=1.00\textwidth]{images/graph/search_dt_pie}

    \caption{Etc}
    \label{fig:sc-pie}
  \end{subfigure}

  \caption{Etc}
\end{figure}

The blue line in Figure \ref{fig:sc-graph} plots the number of users

First increase 69.4\% of users), with a median of 2 searches.
Note that starting at search complexity one or greater counts as a ``searches before first increase value'' of 0.

Second increase (7.9\% of users)
Median: 8 searches
Average: 17.52 searches

DSQL++

>>>>

\subsubsection{Analysis of users with search complexity increases}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.9\textwidth]{images/graph/search_dt}

  \caption{User-tracked search complexity over time}
  \label{fig:sc-graph}
\end{figure}

The blue line in Figure \ref{fig:sc-graph} plots the number of users that had their \emph{first increase} in search complexity per search index (searches \#16--\#25 represent 47 users, and 26+ searches represents only 29 users). The green line plots the number of users for a \emph{second increase} at the given search index (searches \#16--\#25 represent 35 users, and 26+ searches represents 32).

The amount of users whose first searches are of nonzero complexity may be surprising. The vast majority of these are \textbf{title} searches however, which \emph{are} included in the ``complex'' field table. This is purposeful---title searches only represent 8\% of all search field uses, as we saw in Figure \ref{fig:searchtypes} of the section before last. Moreover, a user's understanding and/or intuition that the Skedge search field is free-form and can be used for different search fields simultaneously is already a significant conceptualization of SkedgeQL, albeit a relatively basic field.

\subsubsection{Users with increases vs. users without increases}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.9\textwidth]{images/graph/search_dt_pie}

  \caption{Users with a schedule and more than one search split by their number of increases in search complexity}
  \label{fig:sc-pie}
\end{figure}

\vspace{5pt}

Figure \ref{fig:sc-pie} shows that 69.4\% of Skedge users (\emph{users} here defined as having at least one course bookmarked or added to a schedule, with more than two searches since November 3rd---there are 1889 such users in total) have increased their record search complexity at least once, with a median of 2 searches to do so. Of those users, 18\% of them (12\% of total users) have had a \emph{second} increase in search complexity, with a median of 10 searches to do so. 30\% of users have only searched with the department and course number fields.

I believe this is a strong model for evaluating the friendliness and low learning curve of SkedgeQL, and the results are certainly promising, although further analysis on beginning with nonzero search complexity is needed.

### 2016-04-13 analytics/usage.tex
chapter 4 done

In an attempt to exclude ``stale users,'' we can time-constrain our analysis. In the past month, there were 1,416 visitors to the site and 672 visitors \emph{with schedules}. However, this metric excludes data from seniors who did not have need for Skedge in the past month. Going back to November 3, 2015, course registration day ($\sim$5 months ago), we find 4,647 visitors to the site and 1322 visitors with schedules. Thus, we can estimate that roughly \textbf{one-fifth} of all undergraduates (6,046 students) at the College have added courses on Skedge \cite{undergrads}.

>>>>

In an attempt to exclude ``stale users,'' we can time-constrain our analysis. In the past month, there were 1,416 visitors (unique) to the site and 1,136 visitors \emph{with schedules}. However, this metric excludes data from seniors who did not have a need for Skedge in the past month. Going back since November 3, 2015, course registration day ($\sim$5 months ago), we find 4,647 visitors and 2,209 visitors with schedules. Thus, we can estimate that roughly \textbf{22\%} of undergraduate and graduate students (9,470 total) at the College have added courses on Skedge \cite{undergrads}.

### 2016-04-13 conclusion.tex
chapter 4 done

On behalf of myself and the roughly \emph{one-thousand} students who regularly and voluntarily choose to use Skedge, I urge the University to consider adopting it as an official replacement to CDCS.

@@

As a graduating senior, I cannot commit to continuing the upkeep of server costs and system maintenance for Skedge in the long term, and certainly not indefinitely. For the sake of the University's students, parents, faculty, and staff, I hope that my efforts with Skedge were not in vain and can lead to a substantial refresh of University tools that, most crucially, \textbf{involves a dialogue between the administration, students, and staff}. Thank you.

>>>>

On behalf of myself and the roughly two thousand students who regularly and voluntarily choose to use Skedge, I urge the University to consider adopting it as an official replacement to CDCS.

@@

As a graduating senior, I cannot commit to continuing the upkeep of server costs and system maintenance for Skedge in the long term, and certainly not indefinitely. For the sake of the University's students, parents, faculty, and staff, I hope that my efforts with Skedge were not in vain and can lead to a substantial refresh of University tools that, most crucially, \textbf{involves a dialogue between the administration, students, and staff}. Thank you for reading.
